--- 
title: "Counterexamples of Probability"
author: "Seoncheol Park"
date: "`r Sys.Date()`"
header-includes: \usepackage{amsthm, amsmath, kotex, bm, indentfirst, lmodern, graphicx, hyperref, multicol, footmisc, babel, comment, makeidx}
knit: "bookdown::render_book"
site: bookdown::bookdown_site
documentclass: scrbook
bibliography: [packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: SeoncheolPark/book
papersize: b5
geometry: [inner=0.75in,outer=0.75in, top=0.6in, bottom=0.9in]
linkcolor: Cerulean
citecolor: Fuchsia
urlcolor: RedOrange
toccolor: Black
description: "하루에 한 개씩!"
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
